TBD

### 2018-10-17 manuscript/manuscript.tex
completed draft of results.

We found that food-web complexity altered the slope of the adaptive landscape ($\beta$) in two key ways. First, there were fewer traits under directional selection in the complex (2 of 3) vs. simple food web (3 of 3). For example, in both simple and complex food webs there was directional selection for larger chamber diameters and for adult females to avoid ovipositing on trees with high densities of conspecifics (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}). In the simple food web, we also observed directional selection for smaller clutch sizes, but there was no evidence of selection acting on this trait in the complex food web (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}). The absence of selection on clutch size in the complex food web appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids. Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes (fig.~\ref{Fig:LABEL}).

The second key effect of food-web complexity was to steepen the slope of the adaptive landscape (i.e. increase strength of selection). For example, the magnitude of directional selection in complex vs. simple food webs was \textasciitilde 60\% higher for both chamber diameter and female preference (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}). This result was not due to any difference in the relationship between larva survival and gall phenotype ($\textrm{Simple:coef}_{Diam}=0.02 \ [-0.56,0.60]$; $\textrm{Simple:coef}_{Pref}=-0.16 \ [-0.83,0.61]$), but was due to the fact that the average probability of larval survival was lower in complex (0.44 [0.30,0.58]) vs. simple food webs (0.69 [0.54,0.80]). %Note that although the selection gradient is typically expressed as the covariance between relative fitness ($w$) and phenotype ($z_i$), $\beta_{z_i}=\textrm{cov}(w,z_i)$, it can be rewritten as a function of both absolute fitness ($W$) and mean fitness ($\bar W$), $\beta_{z_i}=\textrm{cov}(W,z_i)/ \bar W$. This alternative expression makes clear that lower survival, and thus mean fitness, will always increase the strength of selection.

@@

Unlike the slope, the curvature of the adaptive landscape ($\gamma - \beta \beta^\text{T}$) is influenced by directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients. Our food-web treatment did not appear to alter correlational selection for any combination of traits and there was no strong evidence that any of these selection gradients differed from zero (fig.~\ref{Fig:LABEL}). Similarly, our food-web treatment did not influence quadratic selection on chamber diameter or clutch size and there was no strong evidence that these selection gradients differed from zero (fig.~\ref{Fig:LABEL}). In contrast, our food-web treatment did alter quadratic selection acting on female preference. Specifically, we found evidence for disruptive selection in the complex food web, but no evidence of disruptive or stabilizing selection in the simple food web (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}). Disruptive selection in the complex food web appeared to be due to the presence of larval parasitoids enhancing the relative fitness of larva occuring on either low or high density trees (fig.~\ref{Fig:LABEL}).

@@

\begin{figure}[h!]
%\includegraphics{FIGURE}
\caption{Selection gradients acting on \textit{Iteomyia} phenotypes. Points and lines correspond to estimated means and 95\% confidence intervals, respectively. Orange and blue colors correspond to estimated gradients in complex and simple food webs, respectively. Yellow colors correspond to selection gradients imposed by larval parasitoids. Note that we only plot selection gradients for larval parasitoids when they differed from egg parasitoids (simple food web).}
\label{Fig:LABEL}
\end{figure}

>>>>

We found that food-web complexity altered the slope of the adaptive landscape ($\beta$) in two key ways. First, there were fewer traits under directional selection in the complex (2 of 3) vs. simple food web (3 of 3). For example, in both simple and complex food webs there was directional selection for larger chamber diameters and for adult females to avoid ovipositing on trees with high densities of conspecifics (fig.~\ref{Fig:Gradients}; fig.~\ref{Fig:FL_1D}). In the simple food web, we also observed directional selection for smaller clutch sizes, but there was no evidence of selection acting on this trait in the complex food web (fig.~\ref{Fig:Gradients}; fig.~\ref{Fig:FL_1D}). The absence of selection on clutch size in the complex food web appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids. Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes (fig.~\ref{Fig:Gradients}).

The second key effect of food-web complexity was to steepen the slope of the adaptive landscape (i.e. increase strength of selection). For example, the magnitude of directional selection in complex vs. simple food webs was \textasciitilde 60\% higher for both chamber diameter and female preference (fig.~\ref{Fig:Gradients}; fig.~\ref{Fig:FL_1D}). This result was not due to any difference in the relationship between larva survival and gall phenotype ($\textrm{Simple:coef}_{Diam}=0.02 \ [-0.56,0.60]$; $\textrm{Simple:coef}_{Pref}=-0.16 \ [-0.83,0.61]$), but was due to the fact that the average probability of larval survival was lower in complex (0.44 [0.30,0.58]) vs. simple food webs (0.69 [0.54,0.80]). %Note that although the selection gradient is typically expressed as the covariance between relative fitness ($w$) and phenotype ($z_i$), $\beta_{z_i}=\textrm{cov}(w,z_i)$, it can be rewritten as a function of both absolute fitness ($W$) and mean fitness ($\bar W$), $\beta_{z_i}=\textrm{cov}(W,z_i)/ \bar W$. This alternative expression makes clear that lower survival, and thus mean fitness, will always increase the strength of selection.

@@

Unlike the slope, the curvature of the adaptive landscape ($\gamma - \beta \beta^\text{T}$) is influenced by directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients. Our food-web treatment did not appear to alter correlational selection for any combination of traits and there was no strong evidence that any of these selection gradients differed from zero (fig.~\ref{Fig:Gradients}). Similarly, our food-web treatment did not influence quadratic selection on chamber diameter or clutch size and there was no strong evidence that these selection gradients differed from zero (fig.~\ref{Fig:Gradients}). In contrast, our food-web treatment did alter quadratic selection acting on female preference. Specifically, we found evidence for disruptive selection in the complex food web, but no evidence of disruptive or stabilizing selection in the simple food web (fig.~\ref{Fig:Gradients}; fig.~\ref{Fig:FL_1D}). Disruptive selection in the complex food web appeared to be due to the presence of larval parasitoids enhancing the relative fitness of larva occuring on either low or high density trees (fig.~\ref{Fig:Gradients}).

@@

\begin{figure}[h!]
\includegraphics{Selection-Gradients-1.png}
\caption{Selection gradients acting on \textit{Iteomyia} phenotypes. Points and lines correspond to estimated means and 95\% confidence intervals, respectively. Orange and blue colors correspond to estimated gradients in complex and simple food webs, respectively. Yellow colors correspond to selection gradients imposed by larval parasitoids. Note that we only plot selection gradients for larval parasitoids when they differed from egg parasitoids (simple food web).}
\label{Fig:Gradients}
\end{figure}
